Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-09-30 referee_report/response_to_referee.txt

From: Dr. Michael Gully-Santiago, on behalf of all coauthors
To: Anonymous referee and topical editor, Applied Optics
Date: Monday, September 21 - Friday September 25, 2015
Re: Response to referee report

Thank you for your referee report and detailed reading of our manuscript, "Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy".  Below I respond to the referee's feedback.

I corrected the accent mark in Fabry-Pérot for all instances of the name.

I corrected these grammatical errors:
- p5. Since silicon is opaque in the optical (range?), the...
- p6. are too small to (be) resolve(d) spatially

I removed the sentence "Our ultimate goal is to bond optics with thicknesses as large as 30 mm.", which we agree is too specific to our application.

I reduced the abstract length by about 40% to make it more concise.

I corrected the title of Section 3.

I entirely removed the paragraph in Section 4, "The Cary 5000 has four operation modes..."

I entirely removed the paragraph in Section 4, "The spectral sampling ranged from..."  (This uncontroversial information is in the nearby table.)

I added a discussion of least squares regression versus Gaussian process regression.

In regards to the comment, "For me Tdsp is missing in eq 5. ( Tmix= f Tg&#43;(1-f)Tdsp )", the referee is correct that the last term in eq. 5 represents the contribution of DSP wafer, however the Tdsp factor has been divided out as described in eq 4.  So the last term could be thought of as (1-f)*Tdsp/Tdsp = (1-f)*1.  The reviewers comment did, however, cause me to revise my description of equation 4 to clarify this point.

In regards to the comment, '5.B: the term "Sample Transport Accessory" is really not adapted...', I have removed the mention of the sample transport accessory, and instead simply described the process of stepping across the sample.

I have now defined temperature, T, before its first use, and have eliminated the Figure 1, which was a plot of the temperature dependence of the refractive index.

In response to the referee's comments on concision, I have cut many lines of text, and in some cases entire paragraphs that I agreed were immaterial to the main idea of the paper.  The manuscript lost at least 2 pages out of the raw 32.  I have motivated more clearly the interest in the MCMC formalism over a conventional least squares technique, now located in section 4- "comparing models to data."  Indeed, I agree that a least squares technique can be applied, but I also note the advantages of the Gaussian process regression technique.  I have posted several references to help the reader reproduce the Gaussian Process regression technique if desired.

Upon inspecting this final submission, it is clear that the manuscript has been much improved from the reviewer's comments, particularly with a clearer 'flow' to the paper.

Best regards,
Dr. Gully-Santiago

### 2015-10-11 MGS_AO_archive/AO_bondedSi.tex
first commit of the two-column version in the latex archive.  begin formatting for ArXiV

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                         File: osa-revtex4-1.tex                             %
%                        Date: April 15, 2013                                 %
%                                                                             %
%                              BETA VERSION!                                  %
%                   JOSA A, JOSA B, Applied Optics, Optics Letters            %
%                                                                             %
%            This file requires the substyle file osajnl4-1.rtx,              %
%                   running under REVTeX 4.1 and LaTeX 2e                     %
%                                                                             %
%                   USE THE FOLLOWING REVTeX 4-1 OPTIONS:                     %
% \documentclass[osajnl,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1}%
%                    %% Use 11pt for Applied Optics                           %
%                                                                             %
%               (c) 2013 The Optical Society of America                       %
%                                                                             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\documentclass[osajnl,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1} %% use 11pt for Applied Optics
\documentclass[osajnl,preprint,showpacs,superscriptaddress,12pt]{revtex4-1} %% use 12pt for preprint option
\usepackage{amsmath,amssymb,graphicx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
%\usepackage{longtable}

@@

\begin{figure}[htbp]
\includegraphics[width=0.40\columnwidth]{figs/fpAbsorbfig_alt}
\caption{Ratio of transmission of a 0.5 mm thick Si wafer to that of a 3.0 mm thick Si puck.  \label{figSiAbsorbfig} We detect Si absorption shortward of $\lambda$ = 1250 nm.  The individual measurements have correlated uncertainties attributable to lamp drift at the level of 0.2\%.  The random uncertainties are typically about 0.02\% per sample, though some wavelength regions (e.g. 1700-1900 nm) demonstrate much greater per sample uncertainties.  Absorption longward of 1250 nm (vertical dashed line) is negligible.}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.40\columnwidth]{figs/etalon_trans.pdf}
\caption{\label{figAbsoluteTrans}The family of normal-incidence curves for transmission as a function of vacuum wavelength for various gap sizes in bonded Si optics.  \emph{Top panel}: Absolute transmission through a Si substrate with no gap (top denim-blue solid curve), and small gaps of axial extent 20 nm (green dashed curve), 35 nm (red dash-dotted curve), and 60 nm (purple dotted curve).  The absolute transmission through Si depends on wavelength since the refractive index depends minutely on wavelength.  The curves assume that multiple reflections within the Si substrates add incoherently as discussed in detail in Appendix \ref{sec:Append-IMRTMM}.  \emph{Middle panel}: The ``Gap Transmission'', $T_g$. The gap sizes and colors are the same as in the top panel.  \emph{Bottom panel}: ``Gap Transmission'' for larger gaps, spanning 0$-$3500 nm.  The 3500 nm sized gap (cyan solid line), demonstrates characteristic Fabry-P\'{e}rot etalon fringes.}
\end{figure}

@@

\begin{figure}[htbp]
\includegraphics[width=1.0\columnwidth]{figs/VS20fineGapCrop.pdf}
\caption{
\label{figVS20pattern}
Veeco optical profiler surface plot and histogram for part VS20-21 in the fine pattern section.  The 100 mm diameter VS20-21 is comprised of two thick silicon wafers.  We patterned three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  The depth was $95 \pm 5\;$nm as indicated by the well-separated peaks in the Veeco profilometry histogram.  The fill factor for this and all mesh patterns was 50\%.  The purpose for these patterns was to have gaps of known axial extent against which we could test the optical metrology technique we describe in this article.}
\end{figure}

\input{tbls/tbl_experiments.tex}

\input{tbls/tbl_meshPatterns.tex}

@@

\begin{figure}[htbp]
\includegraphics[width=0.4\columnwidth]{figs/VS2021_IR_image.pdf}
\caption{
\label{figVS2021_IR_image}
IR image of part VS20-21. Three rectangular mesh areas are apparent (Table \ref{tbl_meshPatterns}).  The coarsest mesh, C, shows substructure, while the medium and fine meshes are indistinguishable at the low resolution of the image.  The three dark spots are bubbles at the interface of the direct bonded Si samples.}
\end{figure}

@@

We measured transmission spectra through the bonded Si samples with an Agilent Cary 5000 UV-Vis-NIR spectrophotometer.  Table \ref{tabCary5000pars} lists the typical measurement settings and tool performance.
\input{tbls/tbl_cary5000Pars.tex}

@@

\input{tbls/tbl_DerivedGapSizes}

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{figs/VG03_corner.pdf}
              \caption{Fitted gap size $d$ and fill factor $f$ for VG03 hole region}
		\label{figVG03_corner}
        \end{subfigure}

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{figs/VG03_f100.pdf}
                \caption{Measured spectrum and fit of VG03 hole region}
                \label{figVG03_f100}
        \end{subfigure}
\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths short-ward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.\label{figVG03full} }
\end{figure}

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{figs/VG03p2_corner.pdf}
              \caption{Fitted gap size $d$ and fill factor $f$ for VG03 petal region}
		\label{figVG03p2_corner}
        \end{subfigure}

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{figs/VG03_f045.pdf}
                \caption{Measured spectrum and fit of VG03 petal region}
                \label{figVG03_f045}
        \end{subfigure}
\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. \label{figVG03part}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=\textwidth]{figs/VG09_12_STA_illustration.pdf}
        \caption{Illustration of VG09-12 sample transport accessory measurement positions. \label{figVG0912_STA_illus} }
    \end{subfigure}
    \begin{subfigure}[b]{0.65\textwidth}
        \includegraphics[width=\textwidth]{figs/VG0912_STA_scan_coarse.pdf}
        \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh \label{figVG0912}}
    \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.\label{figVG12sta}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{figs/VG0912_0gap_corner.pdf}
        \caption{Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh}
	\label{VG0912_0gap_corner}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{figs/VG0912_0gap.pdf}
        \caption{Measured spectrum of VG09-12}
        \label{VG0912_0gap}
    \end{subfigure}
\caption{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.  The blue lines represent individual draws from the Gaussian process model.  
\label{figVG12}}
\end{figure}

@@

\begin{figure}[htbp]
\includegraphics[width=0.8\columnwidth]{figs/F1250_10_filter.pdf}
\caption{\label{figFB1250-10} Filter curve and gap spectra.  The Thorlabs FB1250-10 filter transmission curve is shown as the gray shaded region.  We integrate the gap spectra with this filter curve to relate the deficit of flux in IR imaging with the axial extent of interfacial gaps.}
\end{figure}

\input{tbls/tbl_FB1250.tex}

@@

\begin{figure}[htbp]
\includegraphics[width=0.8\columnwidth]{figs/FB1250-10_integ_trans.pdf}
\caption{\label{figFB1250-10_integ} Integrated transmission through the FB1250-10 filter as a function of interface gap size.  The 99.8\% accuracy achieved in this article is shown as the horizontal dashed line.  Imagers that can achieve 5\% photometric accuracy can detect 40 nm gaps.  This figure assumes uncoated Si substrates.}
\end{figure}

@@

\bibliographystyle{osajnl}
\bibliography{AO_bondedSi}

%\begin{thebibliography}{99}

%% Do not include separate BibTeX files; if BibTeX is used,
%% paste the output (contents of .bbl file) here.

%\end{thebibliography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                         File: osa-revtex4-1.tex                             %
%                        Date: April 15, 2013                                 %
%                                                                             %
%                              BETA VERSION!                                  %
%                   JOSA A, JOSA B, Applied Optics, Optics Letters            %
%                                                                             %
%            This file requires the substyle file osajnl4-1.rtx,              %
%                   running under REVTeX 4.1 and LaTeX 2e                     %
%                                                                             %
%                   USE THE FOLLOWING REVTeX 4-1 OPTIONS:                     %
% \documentclass[osajnl,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1}%
%                    %% Use 11pt for Applied Optics                           %
%                                                                             %
%               (c) 2013 The Optical Society of America                       %
%                                                                             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[osajnl,twocolumn,showpacs,superscriptaddress,11pt]{revtex4-1} %% use 11pt for Applied Optics
%\documentclass[osajnl,preprint,showpacs,superscriptaddress,12pt]{revtex4-1} %% use 12pt for preprint option
\usepackage{amsmath,amssymb,graphicx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
%\usepackage{longtable}

@@

\begin{figure}[htbp]
\includegraphics[width=0.40\columnwidth]{fpAbsorbfig_alt}
\caption{Ratio of transmission of a 0.5 mm thick Si wafer to that of a 3.0 mm thick Si puck.  \label{figSiAbsorbfig} We detect Si absorption shortward of $\lambda$ = 1250 nm.  The individual measurements have correlated uncertainties attributable to lamp drift at the level of 0.2\%.  The random uncertainties are typically about 0.02\% per sample, though some wavelength regions (e.g. 1700-1900 nm) demonstrate much greater per sample uncertainties.  Absorption longward of 1250 nm (vertical dashed line) is negligible.}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.40\columnwidth]{etalon_trans.pdf}
\caption{\label{figAbsoluteTrans}The family of normal-incidence curves for transmission as a function of vacuum wavelength for various gap sizes in bonded Si optics.  \emph{Top panel}: Absolute transmission through a Si substrate with no gap (top denim-blue solid curve), and small gaps of axial extent 20 nm (green dashed curve), 35 nm (red dash-dotted curve), and 60 nm (purple dotted curve).  The absolute transmission through Si depends on wavelength since the refractive index depends minutely on wavelength.  The curves assume that multiple reflections within the Si substrates add incoherently as discussed in detail in Appendix \ref{sec:Append-IMRTMM}.  \emph{Middle panel}: The ``Gap Transmission'', $T_g$. The gap sizes and colors are the same as in the top panel.  \emph{Bottom panel}: ``Gap Transmission'' for larger gaps, spanning 0$-$3500 nm.  The 3500 nm sized gap (cyan solid line), demonstrates characteristic Fabry-P\'{e}rot etalon fringes.}
\end{figure}

@@

\begin{figure}[htbp]
\includegraphics[width=1.0\columnwidth]{VS20fineGapCrop.pdf}
\caption{
\label{figVS20pattern}
Veeco optical profiler surface plot and histogram for part VS20-21 in the fine pattern section.  The 100 mm diameter VS20-21 is comprised of two thick silicon wafers.  We patterned three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  The depth was $95 \pm 5\;$nm as indicated by the well-separated peaks in the Veeco profilometry histogram.  The fill factor for this and all mesh patterns was 50\%.  The purpose for these patterns was to have gaps of known axial extent against which we could test the optical metrology technique we describe in this article.}
\end{figure}

\begin{table}[h!]
\caption{UTexas Si bonding experiments \label{tbl_experiments}}
\begin{center}
    \begin{tabular}{ c c c c c}
    \hline
    Name & Diameter & Thickness & Pattern & Pattern Depth\\ 
    -  & mm & mm & - & nm \\
        \hline
    VG02   & 100 & 3.3 $\times$ 2 &  None  & - \\
    VG03   & 100 & 3.3 $\times$ 2 &  Hole \& Petal & 4000$\pm$200 \\
    VG09-12   & 75   & 1 $\times$ 2 & Mesh C & 49 $\pm$6 \\
    VS20-21   & 100 & 0.8 $\times$ 2 &  Mesh C, M, F & 95 $\pm$5 \\
    \hline
    \end{tabular}
\end{center}
\end{table}

\begin{table}[h!]
\caption{Patterned gap properties \label{tbl_meshPatterns}}
\begin{center}
    \begin{tabular}{ c c c c }
    \hline
    Pattern & Fill Factor & feature size & bulk description \\ 
    - & \% & $\mu$m & - \\ 
    \hline
    Hole   & 100     &  -         & 25 mm diameter hole \\     
    Petal  & $\sim5$ & $\sim$2000 & 2 mm wide lines \\         
    Mesh F & 50      &         40 & 100 $\mu$m square holes, Fig. \ref{figVS20pattern}\\ 
    Mesh M & 50      & 200        & 500 $\mu$m square holes\\ 
    Mesh C & 50      & 620        & 1500 $\mu$m square holes\\     
        \hline
    \end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[htbp]
\includegraphics[width=0.4\columnwidth]{VS2021_IR_image.pdf}
\caption{
\label{figVS2021_IR_image}
IR image of part VS20-21. Three rectangular mesh areas are apparent (Table \ref{tbl_meshPatterns}).  The coarsest mesh, C, shows substructure, while the medium and fine meshes are indistinguishable at the low resolution of the image.  The three dark spots are bubbles at the interface of the direct bonded Si samples.}
\end{figure}

@@

We measured transmission spectra through the bonded Si samples with an Agilent Cary 5000 UV-Vis-NIR spectrophotometer.  Table \ref{tabCary5000pars} lists the typical measurement settings and tool performance.

\begin{table}[h!]
\caption{Summary of Cary 5000 measurement parameters \label{tabCary5000pars}}
\begin{center}
\begin{tabular}{ c c }
\hline
        Parameter (Units) & Value \\ 
\hline
        Spectral sampling interval (nm) & 2.0,10.0 \\
        Spectral resolution (nm) & 5 \\
        Typical measurement range (nm) & 1200-2500 \\
		Mean level drift uncertainty (\%) & 0.20 \\
		Random uncertainty (\%) & 0.02 \\
 		Beam size (mm $\times$ mm) & $2 \times 8$ \\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

\begin{table}[h!]
\caption{Inferred gap sizes and fill factors \label{tbl_DerivedGapSizes}}
\begin{center}
    \begin{tabular}{ c c c c c }
    \hline
    Name & Region & Predicted $d$ & Measured $d$ & $f$ \\
    -  & - & nm & nm & - \\
    \hline
    DSP & -    &   0.0  & $3^{+8}_{-2}$ & $0.260^{+0.456}_{-0.230}$\\
    VG09-12 & Off-Mesh    &   0.0  & $11^{+21}_{-7}$ & $0.25^{+0.46}_{-0.22}$\\
    VG03 & Hole    &   4000 $\pm$ 200  & $3960^{+2}_{-2}$ &  $0.999^{+0.001}_{-0.002}$\\
    VG03 & Petal   &   4000 $\pm$ 200  & $4094^{+4}_{-4}$ &  $0.046^{+0.001}_{-0.001}$\\
    \hline
    \end{tabular}
\end{center}
\end{table}

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{VG03_corner.pdf}
              \caption{Fitted gap size $d$ and fill factor $f$ for VG03 hole region}
		\label{figVG03_corner}
        \end{subfigure}

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{VG03_f100.pdf}
                \caption{Measured spectrum and fit of VG03 hole region}
                \label{figVG03_f100}
        \end{subfigure}
\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths short-ward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.\label{figVG03full} }
\end{figure}

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{VG03p2_corner.pdf}
              \caption{Fitted gap size $d$ and fill factor $f$ for VG03 petal region}
		\label{figVG03p2_corner}
        \end{subfigure}

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{VG03_f045.pdf}
                \caption{Measured spectrum and fit of VG03 petal region}
                \label{figVG03_f045}
        \end{subfigure}
\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. \label{figVG03part}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=\textwidth]{VG09_12_STA_illustration.pdf}
        \caption{Illustration of VG09-12 sample transport accessory measurement positions. \label{figVG0912_STA_illus} }
    \end{subfigure}
    \begin{subfigure}[b]{0.65\textwidth}
        \includegraphics[width=\textwidth]{VG0912_STA_scan_coarse.pdf}
        \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh \label{figVG0912}}
    \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.\label{figVG12sta}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{VG0912_0gap_corner.pdf}
        \caption{Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh}
	\label{VG0912_0gap_corner}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{VG0912_0gap.pdf}
        \caption{Measured spectrum of VG09-12}
        \label{VG0912_0gap}
    \end{subfigure}
\caption{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.  The blue lines represent individual draws from the Gaussian process model.  
\label{figVG12}}
\end{figure}

@@

\begin{figure}[htbp]
\includegraphics[width=0.8\columnwidth]{F1250_10_filter.pdf}
\caption{\label{figFB1250-10} Filter curve and gap spectra.  The Thorlabs FB1250-10 filter transmission curve is shown as the gray shaded region.  We integrate the gap spectra with this filter curve to relate the deficit of flux in IR imaging with the axial extent of interfacial gaps.}
\end{figure}

\begin{table}[h!]
\caption{FB1250-10 integrated gap transmission \label{tbl_FB1250}}
\begin{center}
    \begin{tabular}{ r r}
    \hline
    $d$ & $T_{1250}$\\
    nm  & - \\
    \hline
      0 &                   1.000 \\
      8 &                   0.998 \\
     16 &                   0.991 \\
     24 &                   0.981 \\
     32 &                   0.966 \\
     40 &                   0.948 \\
     48 &                   0.928 \\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[htbp]
\includegraphics[width=0.8\columnwidth]{FB1250-10_integ_trans.pdf}
\caption{\label{figFB1250-10_integ} Integrated transmission through the FB1250-10 filter as a function of interface gap size.  The 99.8\% accuracy achieved in this article is shown as the horizontal dashed line.  Imagers that can achieve 5\% photometric accuracy can detect 40 nm gaps.  This figure assumes uncoated Si substrates.}
\end{figure}

@@

\bibliographystyle{osajnl}
%\bibliography{AO_bondedSi}

\begin{thebibliography}{10}
\newcommand{\enquote}[1]{``#1''}

\bibitem{2006SPIE.6273E..77F}
B.~J. {Frey}, D.~B. {Leviton}, and T.~J. {Madison},
  \enquote{{Temperature-dependent refractive index of silicon and germanium},}
  (2006), vol. 6273 of \emph{Society of Photo-Optical Instrumentation Engineers
  (SPIE) Conference Series}.

\bibitem{PhysRev.108.268}
W.~Spitzer and H.~Y. Fan, \enquote{Infrared absorption in $n$-type silicon,}
  Phys. Rev. \textbf{108}, 268--271 (1957).

\bibitem{PhysRev.78.178}
H.~Y. Fan and M.~Becker, \enquote{Infra-red absorption of silicon,} Phys. Rev.
  \textbf{78}, 178--179 (1950).

\bibitem{doi:10.1117/12.323764}
J.~E. Peters, P.~D. Ownby, C.~R. Poznich, and J.~C. Richter,
  \enquote{Far-infrared absorption of czochralski germanium and silicon,} Proc. SPIE
  \textbf{3424}, 98--105 (1998).

\bibitem{2012SPIE.8450E..2TV}
A.~H. {van Amerongen}, T.~{Agocs}, H.~{van Brug}, G.~{Nieuwland}, L.~{Venema},
  and R.~W.~M. {Hoogeveen}, \enquote{{Development of silicon immersed grating
  for METIS on E-ELT},}  (2012), vol. 8450 of \emph{Society of Photo-Optical
  Instrumentation Engineers (SPIE) Conference Series}.

\bibitem{2010SPIE.7739E.123G}
M.~{Gully-Santiago}, W.~{Wang}, C.~{Deen}, D.~{Kelly}, T.~P. {Greene},
  J.~{Bacon}, and D.~T. {Jaffe}, \enquote{{High-performance silicon grisms for
  1.2-8.0 {$\mu$}m: detailed results from the JWST-NIRCam devices},}  (2010),
  vol. 7739 of \emph{Society of Photo-Optical Instrumentation Engineers (SPIE)
  Conference Series}.

\bibitem{1998AnRMS..28..215G}
U.~{G{\"o}sele} and Q.-Y. {Tong}, \enquote{{Semiconductor Wafer Bonding},}
  Annual Review of Materials Science \textbf{28}, 215--241 (1998).

\bibitem{Masteika2014}
V.~Masteika, J.~Kowal, N.~S.~J. Braithwaite, and T.~Rogers, \enquote{A review
  of hydrophilic silicon wafer bonding,} {ECS} Journal of Solid State Science
  and Technology \textbf{3}, Q42--Q54 (2014).

\bibitem{1986JAP....60.2987S}
M.~{Shimbo}, K.~{Furukawa}, K.~{Fukuda}, and K.~{Tanzawa},
  \enquote{{Silicon-to-silicon direct bonding method},} Journal of Applied
  Physics \textbf{60}, 2987--2989 (1986).

\bibitem{1988JaJAP..27L2364S}
R.~{Stengl}, K.-Y. {Ahn}, and U.~{G{\"o}sele}, \enquote{{Bubble-Free Silicon
  Wafer Bonding in a Non-Cleanroom Environment},} Japanese Journal of Applied
  Physics \textbf{27}, L2364--L2366 (1988).

\bibitem{1995ApPhL..67.3614G}
U.~{G{\"o}sele}, H.~{Stenzel}, T.~{Martini}, J.~{Steinkirchner}, D.~{Conrad},
  and K.~{Scheerschmidt}, \enquote{{Self-propagating room-temperature silicon
  wafer bonding in ultrahigh vacuum},} Applied Physics Letters \textbf{67},
  3614--3616 (1995).

\bibitem{1989JaJAP..28L2141L}
V.~{Lehmann}, K.~{Mitani}, R.~{Stengl}, T.~{Mii}, and U.~{G{\"o}sele},
  \enquote{{Bubble-Free Wafer Bonding of GaAs and InP on Silicon in a
  Microcleanroom},} Japanese Journal of Applied Physics \textbf{28},
  L2141--L2143 (1989).

\bibitem{Horn2009}
G.~Horn, M.~Gabriel, J.~Lesniak, and T.~J. Mackin, \enquote{Detection of
  interfacial gas bubbles in wafer bonded silicon with different surface
  treatments,} J. Electrochem. Soc. \textbf{156}, H27 (2009).

\bibitem{feijoo1994}
D.~Feijo\`o, Y.~J. Chabal, and S.~B. Christman, \enquote{Silicon wafer bonding
  studied by infrared absorption spectroscopy,} Applied Physics Letters
  \textbf{65}, 2548--2550 (1994).

\bibitem{1995ApPhA..61..101R}
M.~{Reiche}, S.~{Hopfe}, U.~{G{\"o}sele}, and Q.~Y. {Tong}, \enquote{{Multiple
  internal reflection spectroscopy of bonded silicon wafers},} Applied Physics
  A: Materials Science \& Processing \textbf{61}, 101--105 (1995).

\bibitem{1996JaJAP..35.2102R}
M.~{Reiche}, S.~{Hopfe}, U.~{G{\"o}sele}, H.~{Strutzberg}, and Q.-Y. {Tong},
  \enquote{{Characterization of Interfaces of Directly Bonded Silicon Wafers: A
  Comparative Study of Secondary Ion Mass Spectroscopy Multiple Internal
  Reflection Spectroscopy, and Transmission Electron Microscopy},} Japanese
  Journal of Applied Physics \textbf{35}, 2102--2107 (1996).

\bibitem{JJAP.37.4197}
H.~Takagi, R.~Maeda, T.~R. Chung, N.~Hosoda, and T.~Suga, \enquote{Effect of
  surface roughness on room-temperature wafer bonding by ar beam surface
  activation,} Japanese Journal of Applied Physics \textbf{37}, 4197--4203
  (1998).

\bibitem{2001JOptA...3...85G}
V.~{Greco}, F.~{Marchesini}, and G.~{Molesini}, \enquote{{Optical contact and
  van der Waals interactions: the role of the surface topography in determining
  the bonding strength of thick glass plates},} Journal of Optics A: Pure and
  Applied Optics \textbf{3}, 85--88 (2001).

\bibitem{1996ApPhL..68.2222T}
H.~{Takagi}, K.~{Kikuchi}, R.~{Maeda}, T.~R. {Chung}, and T.~{Suga},
  \enquote{{Surface activated bonding of silicon wafers at room temperature},}
  Applied Physics Letters \textbf{68}, 2222--2224 (1996).

\bibitem{2000JAP....88.4404H}
W.~{Han}, J.~{Yu}, and Q.~{Wang}, \enquote{{Modeling the dynamics of Si wafer
  bonding during annealing},} Journal of Applied Physics \textbf{88},
  4404--4406 (2000).

\bibitem{1995ApPhL..67..863G}
U.~{G{\"o}sele}, S.~{Hopfe}, S.~{Li}, S.~{Mack}, T.~{Martini}, M.~{Reiche},
  E.~{Schmidt}, H.~{Stenzel}, and Q.-Y. {Tong}, \enquote{{What determines the
  lateral bonding speed in silicon wafer bonding?}} Applied Physics Letters
  \textbf{67}, 863--865 (1995).

\bibitem{2007ApOpt..46.6793H}
J.~Haisma, N.~Hattu, J.~T. C. M.~D. Pulles, E.~Steding, and J.~C.~G. Vervest,
  \enquote{Direct bonding and beyond,} Appl. Opt. \textbf{46}, 6793--6803
  (2007).

\bibitem{2001JAP....89.6013L}
D.~A. {Litton} and S.~H. {Garofalini}, \enquote{{Modeling of hydrophilic wafer
  bonding by molecular dynamics simulations},} Journal of Applied Physics
  \textbf{89}, 6013--6023 (2001).

\bibitem{Mitani1990}
K.~Mitani, V.~Lehmann, and U.~Gosele, \enquote{Bubble formation during silicon
  wafer bonding: causes and remedies,} in \enquote{Solid-State Sensor and
  Actuator Workshop, 1990. 4th Technical Digest., IEEE,}  (1990), pp. 74--77.

\bibitem{doi:10.1080/02786828608959094}
D.~W. Cooper, \enquote{Particulate contamination and microelectronics
  manufacturing: An introduction,} Aerosol Science and Technology \textbf{5},
  287--299 (1986).

\bibitem{2000RScI...71.1869G}
A.~C. {Gracias}, C.~{Kuranaga}, J.~R. {Senna}, and M.~D. {Silva},
  \enquote{{Photoacoustic imaging of voids in direct wafer bonding},} Review of
  Scientific Instruments \textbf{71}, 1869--1872 (2000).

\bibitem{2001opt4.book.....H}
E.~{Hecht}, \emph{{Optics 4th edition}} (Addison-Wesley, 2001).

\bibitem{2007fuph.book.....S}
B.~E.~A. {Saleh} and M.~C. {Teich}, \emph{{Fundamentals of Photonics: Second
  Edition}} (John Wiley, 2007).

\bibitem{2002ApOpt..41.3978K}
C.~C. Katsidis and D.~I. Siapkas, \enquote{General transfer-matrix method for
  optical multilayer systems with coherent, partially coherent, and incoherent
  interference,} Appl. Opt. \textbf{41}, 3978--3987 (2002).

\bibitem{1992JEMat..21..669M}
K.~Mitani and U.~G\"osele, \enquote{Wafer bonding technology for
  silicon-on-lnsulator applications: A review,} Journal of Electronic Materials
  \textbf{21}, 669--676 (1992).

\bibitem{2013sdmm.book.....I}
{\.Z}.~{Ivezi{\'c}}, A.~{Connolly}, J.~{VanderPlas}, and A.~{Gray},
  \emph{{Statistics, Data Mining, and Machine Learning in Astronomy}} (2013).

\bibitem{DFMgp}
D.~{F}oreman Mackey, \enquote{Lab section for a course on gaussian process
  regression,} \url{https://github.com/dfm/gp} (2014).
